### 2022-06-08 article.tex
Add suggestions, thanks  Wout Dillen

A paper contains and/or describes data, where we define
data as 'individual facts, statistics, or items of information, often 
numeric' \cite{glossary2003oecd}.
To ensure unhampered knowledge growth, this data should [TODO: Why? Reference!] 
follow the FAIR 
principles.
The FAIR principles \cite{wilkinson2016fair} are that data should be 
[TODO: there are probably better examples]
Findable (e.g. found by web),
Accessible (e.g. DataDryad and or Zenoda), 
Interoperable (e.g. comma-separated files) 
and Reusable (e.g. work on all operating systems)

@@

A paper in itself is data, as it is a collection of text and
figures that we itself can do measurements upon.
Also here, a paper should be FAIR, 
[TODO: there are probably better examples]
i.e.
Findable (e.g. Google Scholar)
Accessible (e.g. view it online), 
Interoperable (e.g. written in English)
and Reusable (e.g. it is valid to cite and build upon earlier academic papers).
This paper itself will later specify the standpoint that a paper
is metadata (i.e. data about data), instead of paradata (i.e.
data that describes the collection of data)

>>>>

A paper contains and/or describes data, where we define
data as 'individual facts, statistics, or items of information, often 
numeric' \cite{glossary2003oecd}.
To ensure unhampered knowledge growth, this data should [TODO: Why? Reference!] 
follow the FAIR 
principles.
The FAIR principles \cite{wilkinson2016fair} are that data should be 
[TODO: there are probably better examples]
Findable (e.g. found by web),
Accessible (e.g. DataDryad and or Zenodo), 
Interoperable (e.g. plain-text file format, such as comma-separated files) 
and Reusable (e.g. work on all operating systems)

@@

A paper in itself is data, as it is a collection of text and
figures that we itself can do measurements upon.
Also here, a paper should be FAIR, 
[TODO: there are probably better examples]
i.e.
Findable (e.g. having a DOI)
Accessible (e.g. open access publications, i.e. published in a public access
repository), 
Interoperable (e.g. written in English (i.e. the current lingua franca of sciece))
and Reusable (e.g. it is valid to cite and build upon earlier academic papers, 
it is peer-reviewed (i.e. satifies a minimal requirement of quality)).
This paper itself will later specify the standpoint that a paper
is metadata (i.e. data about data), instead of paradata (i.e.
data that describes the collection of data)
